Cross-Loop Optimization of Arithmetic Intensity for Finite Element Local Assembly

### 2014-09-09 TACO-paper-v2/coffee.tex
Add paragraph on compilation time

\subsubsection{On the compilation time}
\label{sec:compile-time}
Firedrake and its various software components (see Figure~\ref{fig:coffee-pipeline}) are implemented in Python and Cython, whereas the generated code is pure C. COFFEE has been written in Python to be naturally integrated within Firedrake. Among the various Firedrake modules, COFFEE is where, in general, the least amount of time is spent. The process of transforming the abstract syntax tree never exceeds ... For example, in X, it takes .., while FFC needed Y secs to translate UFL code into the abstract syntax tree. Being a domain-specific compiler, COFFEE expects C code with a certain structure (e.g. it know there is no control flow), so data-flow analysis for dependency tracking can be kept to a minimum. This is also a clear advantage over a general-purpose compiler.

>>>>

\subsubsection{On the compilation time}
\label{sec:compile-time}
Firedrake and its various software components (see Figure~\ref{fig:coffee-pipeline}) are implemented in Python and Cython, whereas the generated code is pure C. COFFEE has been written in Python to be naturally integrated within Firedrake. Among the various Firedrake modules, COFFEE is where, in general, the least amount of time is spent. The process of transforming the abstract syntax tree usually takes order of milliseconds. For instance, for the Helmholtz equation with $p=4$ on a tiny tetrahedral mesh, it took 0.0009s to transform the abstract syntax tree, while the whole assembly process needed 0.384s. Being a domain-specific compiler, COFFEE expects C code with the structure outlined in Figure~\ref{code:general-structure}, so typical compilers functionalities such as dependency tracking are simplified with respect to a general-purpose compiler, which implies a clear advantage in compilation time and implementation complexity.
